A thermodynamic view of dusty protoplanetary disks

### 2017-05-11 paper.tex
add flow chart in intro to summarize centreal idea

Under these two approximations, we show that the equations of 
isothermal dusty gas dynamics are equivalent to that of adiabatic, pure gas
dynamics. This is because tightly-coupled dust particles are almost
entrained in the gas, which is analogous to the advection
of entropy following an adiabatic fluid. We show that the   
effective entropy of isothermal dusty gas scales with its gas
fraction. Finite dust-gas drag act as effective heating/cooling: the relative
drift between dust and gas causes a fluid parcel to exchange dust
particles with its surroundings; an effect similar to heat exchange
between a gas parcel and its surroundings.

@@

>>>>

Under these two approximations, we show that the equations of 
isothermal dusty gas dynamics are equivalent to that of adiabatic, pure gas
dynamics (Fig. \ref{concept_chart}). This is because tightly-coupled dust particles are almost
entrained in the gas, which is analogous to the advection
of entropy following an adiabatic fluid. We show that the   
effective entropy of isothermal dusty gas scales with its gas
fraction. Finite dust-gas drag act as effective heating/cooling: the relative
drift between dust and gas causes a fluid parcel to exchange dust
particles with its surroundings; an effect similar to heat exchange
between a gas parcel and its surroundings.

@@

\begin{figure}
\tikzstyle{process} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
  \tikzstyle{line} = [draw, -triangle 45,thick]  
  \begin{center}
    \begin{tikzpicture}[node distance=5cm]
      \node[process](ellip){isothermal gas+dust+drag};
      \node[process,right of=ellip, node distance = 5.5cm](gi){pure 
        gas+cooling};
      \path [line](ellip) -- node [yshift=.8em]
      {\textcolor{blue}{equivalent} for} (gi);
      \path [line](gi) -- node [yshift=-.8em] {small particles} (ellip);
    \end{tikzpicture}
 \end{center}
\caption{The central concept of this work. A mixture of small particles
  coupled to isothermal gas behave similarly to an adiabatic, pure gas
  subject to cooling.  This
  permits one to use the equations for standard hydrodynamics to study
  dust-gas dynamics. \label{concept_chart}}
\end{figure}
